HMM Model development

### 2020-05-20 dev/hmm_model_devel.Rmd
Roughly working posterior predictve
Fixing posterior predictive, plots from posterior

```{r}
data <- hmm_simulator(5, 10, 2, use_noisy_states = TRUE)

@@

xx <- brms::posterior_epred(bfit)
dim(xx)
```

>>>>

```{r}
data <- hmm_simulator(20, 15, 2, use_noisy_states = FALSE, N_treatments = 0)

@@

bfit$brmsfit$fit
```

```{r}
#xx <- brms::posterior_epred(bfit) %>% hidden_to_corresponding_observed(bfit$data_processed, .)
xx <- brms::posterior_predict(bfit)

xy <- prediction_to_wide_format(bfit$data, xx)

step_size <- 6
for(step in 1:ceiling(bfit$data_processed$standata$N_series / step_size)) {
  series_id <- ((step - 1) * step_size + 1) : (step* step_size)

  posterior_state_plot(xy, series_id, bfit$data) %>% print()

}
```
